Response to Referees

### 2025-06-25 ms/submission/AuthorComments-egusphere-2025-1046.qmd
address RC1 Technical corrections

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

Thank you. We have removed this sentence and looked to remove similar cases.

@@

Thank you for this suggestion. This opening paragraph is intended to give a brief overview of the full suite of predictors before going into a complete description of how each predictor was derived. We think therefore that it is best placed at the start of the section, but we have tried to improve its readability within the structure (including the mentions of specific predictors).

@@

Thank you.

@@

Thank you. We have clarified that this was the operator's observation and subjective interpretation.

@@

Thank you. We have added some more context to explain the 0.7-cutoff.

@@

Thank you. We have reexamined the formatting of the table.

@@

Thank you for this example. We have gone through the manuscript and revised the language to make it more formal and scientific, while aiming to retain clarity and accessibility. We have removed this phrase and similar casual language throughout the manuscript.

@@

Thank you. Removed.

@@

Thank you. Clarified.

@@

Thank you. We have added a very brief summary of the radiometric surveys to the _Materials and methods_ section, while retaining the reference to an appendix for the full details.

@@

Thank you. We have clarified our statement based on the information in the report by the Geological Survey of Norway.

@@

Revised.

@@

Thank you for this helpful recommendation. We have added a _Conclusions_ section to summarize the key findings of the study. This summary highlights the main results and their implications, which we hope will help readers more easily see how the study addresses its research aims of quantifying predictive accuracy and identifying key predictors.

We have also used this addition to reduce the length of the _Discussion_ section, by reserving some of the more general discussion points for the _Conclusions_.

@@

Thank you for this helpful recommendation. We have added a _Conclusions_ section to summarize the key findings of the study. This summary highlights the main results and their implications, which we hope will help readers more easily see how the study addresses its research aims of quantifying predictive accuracy and identifying key predictors.
